DATA 621 Homework #4

### 2019-11-07 hw4/HW4.Rmd
More work on HW4

hw4_plot <- function(df, var, strip_dollar_signs = FALSE){
  if(strip_dollar_signs){
    df$X <- strip_dollars(df[[var]])
  } else {
    df$X <- df[[var]]
  }
  plot_1 <- ggplot(df, aes(X, TARGET_FLAG, color = TARGET_FLAG)) +
    geom_jitter() +
    scale_color_brewer(palette="Set1") +
    theme_minimal() +
    theme(legend.position = "none",
          axis.title.x = element_blank(),
          axis.title.y = element_blank())

@@

hw4_categorical_plot <- function(df, var, strip_dollar_signs = FALSE){
  if(strip_dollar_signs){
    df$X <- strip_dollars(df[[var]])
  } else {
    df$X <- as.factor(as.character(df[[var]]))
  }
  plot_1 <- ggplot(df, aes(X, TARGET_FLAG, color = TARGET_FLAG)) +
    geom_jitter() +
    scale_color_brewer(palette="Set1") +
    theme_minimal() +
    theme(legend.position = "none",
          axis.title.x = element_blank(),
          axis.title.y = element_blank())

  plot_2 <- df %>%
    filter(TARGET_FLAG == 1) %>%
    ggplot(., aes(X, TARGET_AMT, color = X)) +
      geom_boxplot() +
      scale_color_brewer(palette="Dark2") + #Paired
      theme_minimal() +
      theme(legend.position = "none",
            axis.title.x = element_blank(),
            axis.title.y = element_blank())

  grid.arrange(plot_1, plot_2, ncol=2)
}
```

@@

```{r} 
hw4_categorical_plot(df, "CAR_TYPE")
```

@@

```{r} 
hw4_categorical_plot(df, "CAR_USE")
```

@@

```{r} 
hw4_categorical_plot(df, "CLM_FREQ")
```

@@

**Theoretical Effect**
Unknown effect, but in theory more educated people tend to drive more safely
```{r} 
hw4_categorical_plot(df, "EDUCATION")
```

@@

>>>>

hw4_plot <- function(df, var, strip_dollar_signs = FALSE){
  if(strip_dollar_signs){
    df$X <- strip_dollars(df[[var]])
  } else {
    df$X <- df[[var]]
  }
  plot_1_1 <- ggplot(df, aes(X, TARGET_FLAG, color = TARGET_FLAG)) +
    geom_jitter() +
    scale_color_brewer(palette="Set1") +
    theme_minimal() +
    theme(legend.position = "none",
          axis.title.x = element_blank(),
          axis.title.y = element_blank())

  plot_1 <- ggplot(df, aes(X, color = TARGET_FLAG)) +
    geom_density() + 
    scale_color_brewer(palette="Set1") +
    theme_minimal() +
    theme(legend.position = "none",
          axis.title.x = element_blank(),
          axis.title.y = element_blank())

@@

hw4_categorical_plot <- function(df, var, strip_dollar_signs = FALSE){
  if(strip_dollar_signs){
    df$X <- strip_dollars(df[[var]])
  } else {
    df$X <- as.factor(as.character(df[[var]]))
  }
  plot_1_1 <- ggplot(df, aes(X, TARGET_FLAG, color = TARGET_FLAG)) +
    geom_jitter() +
    scale_color_brewer(palette="Set1") +
    theme_minimal() +
    theme(legend.position = "none",
          axis.title.x = element_blank(),
          axis.title.y = element_blank())
  plot_1 <- df %>%
    group_by(X, TARGET_FLAG) %>%
    tally() %>%
    ggplot(.) +
    geom_bar(aes(X, n, fill = TARGET_FLAG), stat="identity") +
    scale_fill_brewer(palette="Set1") +
    theme_minimal() +
    theme(legend.position = "none",
          axis.title.x = element_blank(),
          axis.title.y = element_blank())
  plot_2 <- df %>%
    filter(TARGET_FLAG == 1) %>%
    ggplot(., aes(X, TARGET_AMT, color = X)) +
      geom_boxplot() +
      scale_color_brewer(palette="Dark2") + #Paired
      theme_minimal() +
      theme(legend.position = "none",
            axis.title.x = element_blank(),
            axis.title.y = element_blank())

hw4_target_table <- function(df, var, strip_dollar_signs = FALSE){
  if(strip_dollar_signs){
    df$X <- strip_dollars(df[[var]])
  } else {
    df$X <- df[[var]]
  }
  df %>%
    group_by(X, TARGET_FLAG) %>%
    tally() %>%
    spread(TARGET_FLAG, n) %>%
    rename(Variable = X) %>%
    kable() %>%
    kable_styling()
}
```

@@

```{r} 
hw4_categorical_plot(df, "CAR_TYPE")
hw4_target_table(df, "CAR_TYPE")
```

@@

```{r} 
hw4_categorical_plot(df, "CAR_USE")
hw4_target_table(df, "CAR_USE")
```

@@

```{r} 
hw4_categorical_plot(df, "CLM_FREQ")
hw4_target_table(df, "CLM_FREQ")
```

@@

**Theoretical Effect**
Unknown effect, but in theory more educated people tend to drive more safely

```{r} 
hw4_categorical_plot(df, "EDUCATION")
hw4_target_table(df, "EDUCATION")
```

@@

### HOMEKIDS

**Theoretical Effect**
Unknown effect

```{r} 
hw4_categorical_plot(df, "HOMEKIDS")
hw4_target_table(df, "HOMEKIDS")
```

**Observed Effect**
It's interesting to note that those with kids have a 0.34 probability of being in an accident.  Those without kids have a 0.22 probability of being in an accident.  This may be useful.

### HOME_VAL

**Theoretical Effect**
In theory, home owners tend to drive more responsibly.

```{r} 
hw4_plot(df, "HOME_VAL", TRUE)
```

**Observed Effect**
There are a lot of zero values.  I am assuming that it is a zero because they are renters.

### INCOME

**Theoretical Effect**
In theory, rich people trend to get into fewer crashes.

```{r} 
hw4_plot(df, "INCOME", TRUE)
```

**Observed Effect**
There are a lot of zero values.  I am assuming that it is a zero because they are renters.

### JOB

**Theoretical Effect**
In theory, white collar jobs tend to be safer

```{r} 
hw4_categorical_plot(df, "JOB")
hw4_target_table(df, "JOB")
```

**Observed Effect**
There is a 0.21 probability for white collar job holders being in an accident.  there's a 0.34 probability for the blue collar jobs.  There may be some truth to the theoretical effect.

### KIDSDRIV

**Theoretical Effect**
When teenagers drive your car, ou are more likely to get into crashes

```{r} 
hw4_categorical_plot(df, "KIDSDRIV")
hw4_target_table(df, "KIDSDRIV")
```

**Observed Effect**
INSERT TEXT HERE
